\Large\textbf{3D Graphics Rendering with OpenGL}

### 2019-03-28 Paper.tex
Fix compile warning

% Margins and page size
\usepackage[a4paper, total={6in, 8in}, margin=1in]{geometry}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.39\textwidth}
    	\includegraphics[width=\textwidth]{cpu}
    	\caption{CPU Architecture.}
    	\label{fig:cpu}
    \end{subfigure}
    \begin{subfigure}[b]{0.39\textwidth}
	    \includegraphics[width=\textwidth]{gpu}
	    \caption{GPU Architecture.}
	    \label{fig:gpu}
    \end{subfigure}
	\caption{A comparison of typical CPU and GPU architectures \cite{larkin2016}.}
	\label{fig:architecture}
\end{figure}

@@

Graphics rendering is done by defining primitives such as points, lines, and triangles in a 3D space. After these points are defined their locations are transformed, and they are drawn on the screen through a process called rasterization \cite{mckesson2018}. Figure \ref{fig:triangle-rendering} shows a simple example of the rasterization process. The figure begins by defining a triangle which is composed of three 3D vectors. The rasterizer then determines which pixels the triangle overlaps through a process called scan conversion. One way to do this is to include pixels if their centers are contained within the element. Rasterization then produces fragments, which is an element that contributes to the final color of a pixel \cite{sellers2016}. The fragments are assigned a color in later steps of the rendering process and which might be changed when effects such as lighting are taken into account.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.29\textwidth}
    	\includegraphics[width=\textwidth]{pipeline}
    	\caption{A simplified OpenGL pipeline \cite{sellers2016}.}
    	\label{fig:pipeline-flow}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
	    \includegraphics[width=\textwidth]{pipeline-visualized}
	    \caption{Visualization of data flowing through the OpenGL pipeline \cite{overvoorde2019}.}
	    \label{fig:pipeline-visualized}
    \end{subfigure}
	\caption{The OpenGL rendering pipeline.}
	\label{fig:pipeline}
\end{figure}

>>>>

% Margins and page size
\usepackage[a4paper, margin=1in]{geometry}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{0.39\textwidth}
    	\includegraphics[width=\textwidth]{cpu}
    	\caption{CPU Architecture.}
    	\label{fig:cpu}
    \end{subfigure}
    \begin{subfigure}[h]{0.39\textwidth}
	    \includegraphics[width=\textwidth]{gpu}
	    \caption{GPU Architecture.}
	    \label{fig:gpu}
    \end{subfigure}
	\caption{A comparison of typical CPU and GPU architectures \cite{larkin2016}.}
	\label{fig:architecture}
\end{figure}

@@

Graphics rendering is done by defining primitives such as points, lines, and triangles in a 3D space. After these points are defined their locations are transformed and they are drawn on the screen through a process called rasterization \cite{mckesson2018}. Figure \ref{fig:triangle-rendering} shows a simple example of the rasterization process. The figure begins by defining a triangle which is composed of three 3D vectors. The rasterizer then determines which pixels the triangle overlaps through a process called scan conversion. One way to do this is to include pixels if their centers are contained within the element. Rasterization then produces fragments, which is an element that contributes to the final color of a pixel \cite{sellers2016}. The fragments are assigned a color in later steps of the rendering process and which might be changed when effects such as lighting are taken into account.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{0.29\textwidth}
    	\includegraphics[width=\textwidth]{pipeline}
    	\caption{A simplified OpenGL pipeline \cite{sellers2016}.}
    	\label{fig:pipeline-flow}
    \end{subfigure}
    \begin{subfigure}[h]{0.49\textwidth}
	    \includegraphics[width=\textwidth]{pipeline-visualized}
	    \caption{Visualization of data flowing through the OpenGL pipeline \cite{overvoorde2019}.}
	    \label{fig:pipeline-visualized}
    \end{subfigure}
	\caption{The OpenGL rendering pipeline.}
	\label{fig:pipeline}
\end{figure}
